---
title: "An example paper"
date: '`r Sys.Date()`'
authors:
  - name: "Kelly L. Sovacool"
    url: https://github.com/kelly-sovacool
    affiliation: Department of Computational Medicine and Bioinformatics, University of Michigan, Ann Arbor, MI
    orcid_id: 0000-0003-3283-829X
  - name: "Patrick D. Schloss"
    url: https://github.com/pschloss
    affiliation: Department of Microbiology and Immunology, University of Michigan, Ann Arbor, MI
bibliography: references.bib
output:
  distill::distill_article:
    toc: true
    toc_float: true
    toc_depth: 3
  pdf_document:
    keep_tex: false
    includes:
      in_header: preamble.tex
      before_body: head.tex
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "docs", output_format = "all") })
csl: msystems.csl
fontsize: 12pt
geometry: margin=1.0in
repository_url: https://github.com/SchlossLab/gh-tips
creative_commons: CC BY-SA
twitter:
  creator: "@kelly_sovacool"
  site: "@PatSchloss"
---

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE}
mothuR::set_knitr_opts()
```

```{r deps, message = FALSE}
library(here)
library(mothuR)
library(tidyverse)
```

## Abstract

Distill is a publication format for scientific and technical writing, native to the web. 
The HTML version of this document is in distill format, 
while the PDF version is styled with LaTeX.
Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.

Here are some example citations [@westcott_opticlust_2017; @schloss_introducing_2009].

## Author Contributions {.appendix}

You can put sub-headings in the appendix, such as an author contribution statement.
Here's where you would summarize what each author contributed to the study.